Reproducible Summary Tables with the \pkg{gtsummary} Package

### 2021-07-17 gtsummary_submission.tex
overleaf

The \code{tbl\_regression()} function leverages the huge effort behind the \pkg{broom} and \CRANpkg{broom.helpers} packages to perform the initial formatting of the regression object \citep{broom,broom.helpers}.
Because \code{tbl\_regression()} utilizes \code{broom::tidy()}, there are many model types that are supported out of the box, such as \code{lm()}, \code{glm()}, \code{lme4::lmer()}, \code{lme4::glmer()}, \code{geepack::geeglm()}, \code{survival::coxph()}, \code{survival::survreg()}, \code{survival::clogit()}, \code{nnet::multinom()}, \code{rstanarm::stan\_glm()}, models built with the \pkg{mice} package \citep{mice}, and many more.
A custom tidier may be specified as well, which is helpful when you need to present non-standard modifications to your model results such as Wald confidence intervals or results with modified variance-covariance standard errors.

@@

We love themes.
The default styling (e.g., statistics displayed in \code{tbl\_summary()}, how \emph{p}-values are rounded, decimal separator, and more) follow the reporting guidelines from European Urology, The Journal of Urology, Urology, and the British Journal of Urology International \citep{assel2019guidelines}.
However, you will likely submit to another journal, or your personal preferences differ from the defaults.
The \pkg{gtsummary} package is unique from other table building packages in the ability to set fine-grained customization defaults with themes.
Themes were created to make these customizations easy to navigate and reuse across documents or projects.
With themes, users can control default settings for existing functions (e.g., always present means instead of medians in \code{tbl\_summary()}), as well as other changes that are not modifiable with function arguments.
Several themes are available to follow various journals' reporting guidelines, reduce cell padding and font size, and language themes to translate \pkg{gtsummary} tables to more than 14 languages.

@@

>>>>

The \code{tbl\_regression()} function leverages the huge effort behind the \pkg{broom}, \CRANpkg{parameters} \citep{parameters}, and \CRANpkg{broom.helpers} \citep{broom.helpers} packages to perform the initial formatting of the regression object.
Because \code{tbl\_regression()} utilizes these packages, there are many model types that are supported out of the box, such as \code{lm()}, \code{glm()}, \code{lme4::lmer()}, \code{lme4::glmer()}, \code{geepack::geeglm()}, \code{survival::coxph()}, \code{survival::survreg()}, \code{survival::clogit()}, \code{nnet::multinom()}, \code{rstanarm::stan\_glm()}, models built with the \pkg{mice} package \citep{mice}, and many more.
A custom tidier may be specified as well, which is helpful when you need to present non-standard modifications to your model results such as Wald confidence intervals or results with modified variance-covariance standard errors.

@@

We love themes.
The default styling (e.g., statistics displayed in \code{tbl\_summary()}, how \emph{p}-values are rounded, decimal separator, and more) follow the reporting guidelines from European Urology, The Journal of Urology, Urology, and the British Journal of Urology International \citep{assel2019guidelines}.
However, you will likely submit to another journal, or your personal preferences differ from the defaults.
The \pkg{gtsummary} package is unique from other table building packages with the ability to set fine-grained customization defaults with themes.
Themes were created to make these customizations easy to navigate and reuse across documents or projects.
With themes, users can control default settings for existing functions (e.g., always present means instead of medians in \code{tbl\_summary()}), as well as other changes that are not modifiable with function arguments.
Several themes are available to follow various journals' reporting guidelines, reduce cell padding and font size, and language themes to translate \pkg{gtsummary} tables to more than 14 languages.

@@

The language theme can be used to translate the table to another language and allows users to specify the decimal and big mark symbols.
For example, \code{theme\_gtsummary\_language(language = "es", decimal.mark = ",", big.mark = ".")} will translate the output to Spanish and format numeric results as \code{1.000,00} instead of \code{1,000.00} (the default formatting).
